Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-08 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2, Comment A, Part 1: Make the language of definition 2 match with the language of the calculus

\begin{definition} \emph{Terms and formulas} are given by the following grammar:
\begin{align*}
 s,t \quad ::= \quad & 
  p_\tau \ \mid \ 
  X_\tau \ \mid \
  (\lambda X_\theta.s_\tau)_{\theta\imp\tau} \ \mid \ 
  (s_{\theta\imp\tau}\, t_\theta)_\tau \ \mid \\
  & s_{\tau} = t_{\tau} \ \mid \\
& \bot_o \ \mid \
  \imp_{o\imp o\imp o} \ \mid \ 
  \wedge_{o\imp o\imp o} \ \mid \
  \vee_{o\imp o\imp o} \ \mid \\
& \all_{(\tau\imp o)\imp o} \ \mid \ 
  \ex_{(\tau\imp o)\imp o} \ \mid \
  \nec_{o\imp o} \ \mid \
  \pos_{o\imp o}
\end{align*}
where $p_\tau$ and $X_\tau$ range over, respectively, constants and variables of type $\tau$. Parenthesis conventions, infix notation for propositional connectives and binding notation for quantifiers are assumed. Furthermore, subscript types are omitted when they are clear from the context. Inequality ($\neq_{\tau\imp\tau\imp o}$), negation ($\neg_{o\imp o}$) and equivalence ($\biimp_{o\imp o\imp o}$) are defined by $s \neq t\equiv \neg (s=t)$, $\neg A\equiv A\imp \bot$ and $ (A\biimp B)\equiv (A\imp B)\wedge (B\imp A)$.
\end{definition}

>>>>

\begin{definition} \emph{Terms and formulas} are given by the following grammar:
\begin{align*}
 s,t \quad ::= \quad & 
  p_\tau \ \mid \ 
  X_\tau \ \mid \
  (\lambda X_\theta.s_\tau)_{\theta\imp\tau} \ \mid \ 
  (s_{\theta\imp\tau}\, t_\theta)_\tau \ \mid \\
  & s_{\tau} = t_{\tau} \ \mid \\
& \bot_o \ \mid \
  \imp_{o\imp o\imp o} \ \mid \ 
  \wedge_{o\imp o\imp o} \ \mid \\
& \all_{(\tau\imp o)\imp o} \ \mid \ 
  \ex_{(\tau\imp o)\imp o} \ \mid \
  \nec_{o\imp o} \ \mid \
  \pos_{o\imp o}
\end{align*}
where $p_\tau$ and $X_\tau$ range over, respectively, constants and variables of type $\tau$. Parenthesis conventions, infix notation for propositional connectives and binding notation for quantifiers are assumed. Furthermore, subscript types are omitted when they are clear from the context. Inequality ($\neq_{\tau\imp\tau\imp o}$), negation ($\neg_{o\imp o}$), disjunction ($\vee_{o\imp o\imp o}$) and equivalence ($\biimp_{o\imp o\imp o}$) are defined by $s \neq t\equiv \neg (s=t)$, $\neg A\equiv A\imp \bot$, $(A \vee B) \equiv \neg (\neg A \wedge \neg B)$ and $ (A\biimp B)\equiv (A\imp B)\wedge (B\imp A)$.
\end{definition}
